---
title: "San Francisco Rentals"
author: "Buy R House: Vania Fong, Matthew Gunson, and Mia Nakajima"
font-family: 'Helvetica'
date: "May 4, 2017"
output: 
  slidy_presentation:
    incremental: true
runtime: shiny

---

## Question and Data

- How do various features of an apartment or house affect the rent in San Francisco and which features have the greatest effect on the rent?

- We formed our data set by scraping listings from [zillow](www.zillow.com).
Limiting the scrape to only houses and apartments for rent in San Francisco, CA on April 25, 2017.

- We think the most highly correlated feature to price will be the size, but we also looking at the following features:

a) Zip Code

b) House vs. Apartment

c) Number of Bedrooms/Bathrooms

d) If Pets are allowed

e) Parking

f) Laundry Availability

g) Cooling and/or Heating

---

```{r, echo = FALSE}
library(shiny)
shinyAppDir("~/Desktop/SpringStat133/Stat133Project/Final_Shiny",
  options=list(
    width="100%", height=700
  )
)
df <- read.csv("~/Desktop/SpringStat133/Stat133Project/tidy.csv")
```

```{r, echo=FALSE}
coef <- coef(lm(df$Monthly_Rent_USD ~ df$Bathrooms))
paste("Linear Coefficients in Approximately Linear Association Between Rent and Bathrooms")
paste("Y Intercept = ", coef[1])
paste("Slope = ", coef[2])
```

---

```{r, echo=FALSE, message=FALSE}
library(DataComputing)
library(dplyr)
library(ggplot2)
library(statisticalModeling)
library(rpart)
library(rpart.plot)
df <- read.csv("~/Desktop/SpringStat133/Stat133Project/tidy.csv")
rpart(Monthly_Rent_USD ~ Pets + Building, data=df, cp = 0.04) %>% rpart.plot::prp(type=3)
rpart(Monthly_Rent_USD ~ Bathrooms + Bedrooms, data=df, cp = 0.09) %>% rpart.plot::prp(type=3)
rpart(Monthly_Rent_USD ~ Building + Cooling + Heating, data=df, cp = 0.03) %>% rpart.plot::prp(type=3)
```

---

## Methods and Conclusions

- We found that Bathrooms and Rent had the greatest correlation coefficient
- Bathrooms and Rent seemed to be the variables most linearly associated 
- Rpart findings

