---
title: "San Francisco Rentals"
author: "Buy R House: Vania Fong, Matthew Gunson, and Mia Nakajima"
font-family: 'Helvetica'
date: "May 4, 2017"
output: 
  slidy_presentation:
    incremental: true
runtime: shiny

---

## Questions, Data, and Methods

- How do features of an apartment or house affect the rent in San Francisco and which features have the most measureably linear relationship with the rent?

- We formed a data set of 773 observations by scraping listings from [zillow](www.zillow.com).
Limited the scrape to only houses and apartments for rent in San Francisco, CA on April 25, 2017.  

- Prior Assumption: The feature with the greatest correlation to price will be the square footage, we test this hypothesis by examining the following features:

a) Zip Code

b) House vs. Apartment

c) Number of Bedrooms/Bathrooms

d) If Pets are allowed

e) Parking

f) Laundry facilities

g) Cooling and/or Heating

---

```{r, echo = FALSE, message=FALSE}
setwd(dir="~/Desktop/SpringStat133/Stat133Project")
getwd()
library(shiny)
library(DataComputing)
library(dplyr)
library(ggplot2)
library(statisticalModeling)
library(rpart)
library(rpart.plot)
shinyAppDir("~/Desktop/SpringStat133/Stat133Project",
  options=list(
    width="100%", height=700
  )
)
```


```{r,echo=FALSE,message=FALSE}
df <- read.csv("tidy.csv")
print("Rent by Pets and Building Type")
rpart(Monthly_Rent_USD ~ Pets + Building, data=df, cp = 0.04) %>% rpart.plot::prp(type=3)
```

```{r,echo=FALSE,message=FALSE}
print("Rent by Number of Bathrooms and Bedrooms")
rpart(Monthly_Rent_USD ~ Bathrooms + Bedrooms, data=df, cp = 0.09) %>% rpart.plot::prp(type=3)
```

```{r,echo=FALSE,message=FALSE}
print("Rent by Building Type, Cooling, and Heating appliances")
rpart(Monthly_Rent_USD ~ Building + Cooling + Heating, data=df, cp = 0.03) %>% rpart.plot::prp(type=3)
```

---

## Conclusions

```{r, echo=FALSE, message=FALSE}
data1 <- read.csv("tidy.csv")

correlations <- c()
for (i in c( 5, 6, 7)){
  
  df <- data.frame(data1$Monthly_Rent_USD, data1[[i]])
  correlation <- cor(df, use = "pairwise.complete.obs")
  correlations <- c(correlations, correlation[[2]])
  
}

names(correlations) = c("Bedrooms", "Bathrooms", "Area_SqFt")
correlations
```

Correlation of rent vs number of bathrooms is the greatest at r = .635


```{r, echo=FALSE, message=FALSE}

df <- read.csv("tidy.csv")
coef <- coef(lm(df$Monthly_Rent_USD ~ df$Bathrooms))
paste("Y Intercept = ", coef[1])
paste("Slope = ", coef[2])

```

Linear Coefficients in Approximately Linear Association Between Rent and number of Bathrooms


- We found that Bathrooms and Rent had the greatest correlation coefficient and the strongest linear association.

a) Correlation and Least Squares Coefficients

b) Approximately linear loess fit

- Number of bathrooms are a better for predicting rent than number of bedrooms 

- Places that do not allow pets tend to be more expensive according to the scatterplots and partitioned trees

- Due to characteristics of the real estate market the relationship between rent and many of the variables we considered should not be modeled using linear least squares.

a) Need more data to capture the relationship between the variables examined in this analysis.